### 2013-01-28 mcmc.tex
More comments, prefaced by my initials
Names for evidence

\begin{abstract}
Markov Chain Monte Carlo (MCMC) methods for sampling probability
distribution functions, plus abundant computational resources,
have transformed
the sciences.
Here we give a fast overview of basic MCMC methods and then turn to
practical advice for their use in real inference problems.
We give advice on method choice, tuning for performance,
initialization and burn-in, judging convergence, and use of the chain
output to make results {\it with error bars}.
% Giving MCMC results with error bars is uncommon, but cool. I thought it
% deserved an italic
[Insert some generally useful point here!]
\end{abstract}

@@

Markov Chain Monte Carlo (MCMC) methods are methods for sampling
probability distribution functions (pdfs).
% pdf usually stands for probability density function. You are using non-standard
% terminology here.
They don't require that you have a full analytic description of the
properly normalized pdf for sampling to proceed; they only require
that you be able to compute ratios of the pdf at pairs of locations.
These properties make MCMC methods ideal for sampling \emph{posterior
  pdfs} in probabilistic inferences:
In probabilistic inferences, the posterior pdf $p(\pars\given\data)$,
or pdf for the parameters $\pars$ given the data $\data$, is
constructed from the likelihood $p(\data\given\pars)$, or pdf for the
data given the parameters, and the prior pdf $p(\pars)$ for the
parameters by what's often known as ``Bayes rule'',
\begin{eqnarray}
p(\pars\given\data) &=& \frac{1}{Z}\,p(\data\given\pars)\,p(\pars)
\quad .
\end{eqnarray}
In these contexts, the constant $Z$ is sometimes written as
$p(\data)$, is sometimes called the ``evidence'' or the ``Bayes
integral'', and is usually \emph{extremely hard to
  calculate}.\note{Say words about why we call it $Z$ not $p(\data)$
  and why it is extremely hard to calculate.}
That is, you often know the function $p(\pars\given\data)$ up to a
constant factor; you can compute ratios of the pdf at pairs of points,
but not the precise value at any individual point.

>>>>

\begin{abstract}
Markov Chain Monte Carlo (MCMC) methods for sampling probability
distribution functions, plus abundant computational resources,
have transformed
the sciences.
Here we give a fast overview of basic MCMC methods and then turn to
practical advice for their use in real inference problems.
We give advice on method choice, tuning for performance,
initialization and burn-in, judging convergence, and use of the chain
output to make results {\it with error bars}.
% ******* BJB
% Giving MCMC results with error bars is uncommon, but cool. I thought it
% deserved an italic
[Insert some generally useful point here!]
\end{abstract}

@@

Markov Chain Monte Carlo (MCMC) methods are methods for sampling
probability distribution functions (pdfs). These pdfs may be either probability
mass functions on a discrete space, or probability densities on a continuous
space.
% ******* BJB
% pdf usually stands for probability density function. You are using non-standard
% terminology here. My words above might be too technical given the aim of your
% document.
They don't require that you have a full analytic description of the
properly normalized pdf for sampling to proceed; they only require
that you be able to compute ratios of the pdf at pairs of locations.
These properties make MCMC methods ideal for sampling \emph{posterior
  pdfs} in probabilistic inferences:
% ******** BJB
% I know you don't like it, but LOTS of people use and understand the word
% Bayesian.
In probabilistic inferences, the posterior pdf $p(\pars\given\data)$,
or pdf for the parameters $\pars$ given the data $\data$, is
constructed from the likelihood $p(\data\given\pars)$, or pdf for the
data given the parameters, and the prior pdf $p(\pars)$ for the
parameters by what's often known as ``Bayes rule'',
\begin{eqnarray}
p(\pars\given\data) &=& \frac{1}{Z}\,p(\data\given\pars)\,p(\pars)
\quad .
\end{eqnarray}
% ********* BJB
% Unfortunately there are many more names for the evidence. I prefer
% marginal likelihood myself.
In these contexts, the constant $Z$, sometimes written as
$p(\data)$, is known by the names ``evidence'', ``marginal likelihood''
the ``Bayes integral'' and ``prior predictive probability'', and is usually
\emph{extremely hard to
  calculate}.\note{Say words about why we call it $Z$ not $p(\data)$
  and why it is extremely hard to calculate.}
That is, you often know the function $p(\pars\given\data)$ up to a
constant factor; you can compute ratios of the pdf at pairs of points,
but not the precise value at any individual point.
